---
title: "Project Proposal"
subtitle: "due October 11, 2021 by 11:59 PM "
author: "Isabelle Xiong and Maya Ghanem"
date: "10/10/2021"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

# Load Packages

```{r setup, include=FALSE, echo= FALSE, message= FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load data packages, warning= FALSE, message= FALSE}
library(readr)
library(tidyverse)
library(readxl)
library(dplyr)
```

```{r install spatial data packages}
library(sf)
library(rgeos)
library(scales)
library(maps)
theme_set(theme_bw())
```

# Load Data

```{r load-data}
Carolina_Small_Business_Dataset <- read_excel("~/Carolina Small Business: Stats 198 Project/data/Carolina Small Business Dataset.xlsx")
```

```{r spatial map}
map('county','north carolina')
```

```{r spatial map data frame}
north_carolina_map <- map_data('county', 'north carolina')
```

# Introduction and Data, including Research Questions

(The introduction should introduce your general research question and your data (where it came from, how it was collected, what are the cases, what are the variables, etc.). Your research questions should be clearly specified. The motivation for your research question should be clear, with citations to relevant literature as appropriate.)

Research Questions:

1) Is more money lent to minority and women owned businesses? Is the difference in lending money significant based on whether a business is minority and/or women owned?

2) Is there a difference in social, community trust, and financial stability scores based on whether the business is minority and/or women owned?

3) What do employment outcomes look like for minority owned and women owned businesses versus businesses that are not minority or women owned?

# Glimpse

Here is a glimpse of our dataset:

```{r glimpse dataset}
glimpse(Carolina_Small_Business_Dataset)
```

# Data Analysis Plan

(Specify the outcome (response, Y) and predictor (explanatory, X) variables you will use to answer your question, as well as the comparison groups you will use, if applicable. You may include very preliminary exploratory data analysis, including some summary statistics and visualizations, along with some explanation on how they help you learn more about your data. Note the statistical method(s) that you believe will be useful in answering your question(s). 
What results from these specific statistical methods are needed to support your hypothesized answer?)

# References
