---
title: "Project Proposal Revised"
subtitle: "due October 20, 2021 by 11:59 PM "
author: "Isabelle Xiong and Maya Ghanem"
date: "10/17/2021"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo= FALSE, message= FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages('tidyverse')
```

```{r load-data-packages, echo= FALSE, warning= FALSE, message= FALSE}
library(readr)
library(tidyverse)
library(readxl)
library(dplyr)
```

```{r install-spatial-data-packages, echo= FALSE, warning= FALSE, message= FALSE}
library(sf)
library(rgeos)
library(scales)
library(maps)
theme_set(theme_bw())
```

# Load Data

# Introduction and Data, including Research Questions

## Motivation for research: 

## Research Questions:

# Glimpse

# Data Analysis Plan

For the research questions, the explanatory and response variables are as follows:

The data analysis methodology is as follows:

## Step 1: Contextualize and Situate the Data

## Step 2: Conduct Statistical Tests

## Step 3: Display Results of Statistical Tests

## Step 4: Draw Conclusions

# References
